Target Markdown

### 2023-12-06 _targets.Rmd
Update figures with new sims

        select(-productivity) %>%

@@

      w_avg_tlvl = c(1.5, 2, 3),
      Z = c(10, 100),

@@

      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)

@@

@@

      "w_avg_tlvl" = 2,

@@

              seq(0.01, 0.2, length.out = 50),
              seq(1.5, 3.5, length.out = 50),
              seq(.02, .3, length.out = 50)

@@

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_prod_bm,
      sim_fw %>%
        filter(bm_total > 10^-5) %>%
        ggplot(aes(x = as.factor(productivity), y = log(bm_total))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Total biomass") +
        theme_bw()
      ),
    tar_target(p_prod_pop_stab,
      sim_fw %>%
        ggplot(aes(x = as.factor(productivity), y = log(pop_stab))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Population stability") +
        theme_bw()
    ),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        p_prod_bm,
        p_prod_pop_stab,
        labels = "auto"
      )

@@

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

@@

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

@@

```{r tar-make}
tar_make()
```

@@

@@

@@

```{r}
tar_load(pred_data)
p_pred_sr_resp_div_int_env <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    resp_div %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 2.0
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(resp_div),
      fill = as.factor(resp_div),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = .8) +
  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(
    cols = vars(env_stoch),
    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation", fill = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

#pred_data$async <- predict(mod_tot_async, newdata = pred_data)
#pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)

```{r}
pred_data_sr_fw <- pred_data %>%
  filter(
    ct_alive %in% c(.1, .3),
    resp_div %in% c(1, .25),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    env_stoch == .1,
    w_avg_tlvl %in% c(2.0, 3.0)
    ) %>%
mutate(
  group_ct_alive = case_when(
    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_avg_int_strength = case_when(
    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    ),
  group_w_avg_tlvl = case_when(
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
    )) %>%
pivot_longer(starts_with("group_")) %>%
filter(!is.na(value)) %>%
mutate(
  name = str_remove(name, "group_"),
  resp_div_cat = str_replace_all(resp_div, resp_div_replacement())
)

@@

```{r}
p_pred_sr <- plot_grid(
  p_pred_data_sr_fw + theme(legend.position = "right"),
  p_pred_sr_resp_div,
  nrow = 2,
  rel_heights = c(.7, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .7,
  units = "mm")
```

@@

sim_fw %>%
  filter(env_stoch == 0.3, rho %in% c(0, .5, 1), productivity == 5) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .6, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .3, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0, bm_total > 10^-5) %>%
  ggplot(aes(x = as.factor(Z), y = bm_total, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = evenness_sae, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = cpe_int, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()
```

>>>>

@@

      w_avg_tlvl = c(1.0, 1.5, 2.3),
      Z = c(1, 10, 100),

@@

      w_avg_tlvl = seq(1.0, 2.5, length.out = 50)

@@

      "ct_alive" = .1,

@@

      "w_avg_tlvl" = 1,

@@

              seq(0.01, 0.1, length.out = 50),
              seq(1.0, 2.5, length.out = 50),
              seq(.02, .35, length.out = 50)

@@

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        labels = "auto"
      )

@@

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

@@

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), env_stoch == .5) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), env_stoch == .5) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

@@

```{r tar-make}
tar_make()
tar_make_future(workers = 3)
```

@@

```{r debug, eval = FALSE}
tar_load(sim_fw)
ti <- sim_fw %>%
  mutate(across(c(stab_com, richness), log)) %>%
  mutate(across(c(sim_id, fw_id), as.factor)) %>%
  mutate(
    across(c(stab_com, richness,
        env_stoch, resp_div, Z,
        ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
      ~scale(.x)[, 1])
  )
tar_load(stab_com_part_var)
tu <- map(stab_com_part_var,
  ~glmmTMB(formula_stab_fw_model(
      resp = .x,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"
      ),
    data = ti
    ))
```

@@

```{r plot-sim}
load(here("data", "sim_for_plot"))
length(unique(sim_for_plot$sim_id))
sim_for_plot %<>%
  left_join(
    tar_read(sim_fw)
  )
stoch <- 0.3
hill <- 2
env_corr <- 0
unique(sim_for_plot$env_stoch)
```

```{r}
sim_for_plot %>%
  filter()

```{r}
sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
  arrange(fw_id)
low_z_low_rich <- sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr, richness == 10) %>%
  arrange(desc(max_tlvl), richness)
tu <- timespecies_mat_to_long_tibble(low_z_low_rich$species[[1]])
plot_timeseries_lg_tbl(tu)
```

```{r}
low_z_high_rich <- sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
  # For plotting purpose, not too much species
  filter(richness > 15) %>%
  arrange(desc(max_tlvl), desc(richness))

low_z_high_rich_mat <- get_mat_list(low_z_high_rich)
plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(low_z_high_rich_mat[[2]]))
```

```{r}
sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 100,
    rho == env_corr, richness == 10) %>%
  arrange(desc(max_tlvl))
high_z_low_rich <- sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 100,
    rho == env_corr, richness == 10) %>%
  arrange(desc(max_tlvl))

plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_low_rich$species[[3]]))
```

```{r}
sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
  # For plotting purpose, not too much species
  filter(richness <= 20) %>%
  arrange(desc(max_tlvl))
high_z_high_rich <- sim_for_plot %>%
  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
  # For plotting purpose, not too much species
  filter(richness == 20) %>%
  arrange(desc(max_tlvl))
plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_high_rich$species[[3]]))
```

```{r}
sim_for_plot$int_strength[[1]] %>% dim
p_low_z_low_rich <- plot_sim(x = sim_for_plot,
  id = low_z_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .3,
  tmax = 200
)
p_low_z_high_rich <- plot_sim(x = sim_for_plot,
  id = low_z_high_rich$sim_id[[2]],
  col_palette = NULL,
  node_size_scale = .5
)
p_high_z_low_rich <- plot_sim(
  x = sim_for_plot,
  id = high_z_low_rich$sim_id[[5]],
  col_palette = NULL,
  node_size_scale = .3)
p_high_z_high_rich <- plot_sim(
  x = sim_for_plot,
  id = high_z_high_rich$sim_id[[3]],
  col_palette = NULL,
  node_size_scale = .4
)

word_label_size <- 11
p_sim_example <- plot_grid(
  p_low_z_low_rich + draw_label(
    "Low PPMR", fontface = 'bold', x = 0, y = .5,
    hjust = .5, vjust = 1, angle = 90, size = word_label_size) +
  draw_label("Low richness", fontface = 'bold', x = 0.5, y = 1,
    hjust = 0.5, vjust = 1, angle = 0, size = word_label_size),
  p_low_z_high_rich + draw_label("High richness", fontface = 'bold', x = 0.5, y = 1,
    hjust = 0.5, vjust = 1, angle = 0, size = word_label_size),
  p_high_z_low_rich + draw_label(
    "High PPMR", fontface = 'bold', x = 0, y = .5,
    hjust = .5, vjust = 1, angle = 90, size = word_label_size),
  p_high_z_high_rich,
  labels = c("b", "", "", ""),
  align = "hv"
)

ggsave_multiple(
  paste0("p_sim_example", c(".png", ".pdf")),
  plot = p_sim_example,
  path = here::here("report", "figures"),
  scale = 2.6,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm")
```

```{r}
sim_for_plot %>%
  filter(Z == 100, env_stoch == 0.3, rho %in% c(0, 1), S == 10, h == 2) %>%
  group_by(fw_id) %>%
  summarise(n = n()) %>%
  filter(n > 1)
sim_for_plot %>%
  filter(env_stoch == 0.3, rho %in% c(0, 1), S == 10, h == 3) %>%
  group_by(fw_id) %>%
  summarise(n = n()) %>%
  filter(n > 1)
fwid <- 6
z <- 10
sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2)

high_resp_div_low_rich <- sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 0)
  #filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
  #arrange(desc(async))
p_high_resp_div_low_rich <- plot_sim(
  x = sim_for_plot,
  id = high_resp_div_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .2,
  title = "High response diversity"
)

low_resp_div_low_rich <- sim_for_plot %>%
  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 1) %>%
  arrange(desc(async))
p_low_resp_div_low_rich <- plot_sim(
  x = sim_for_plot,
  id = low_resp_div_low_rich$sim_id[[1]],
  col_palette = NULL,
  node_size_scale = .2,
  title = "Low response diversity"
)

p_sim_rho_example <- plot_grid(
  p_low_resp_div_low_rich,
  p_high_resp_div_low_rich,
  labels = c("a", ""),
  align = "hv"
)
ggsave_multiple(
  paste0("p_sim_rho_example", c(".png", ".pdf")),
  plot = p_sim_rho_example,
  path = here::here("report", "figures"),
  scale = 2.6,
  dpi = 400,
  width = 80,
  height = 80 * .3,
  units = "mm")
```

```{r}
p_methods <- plot_grid(p_sim_rho_example, p_sim_example, nrow = 2, rel_heights = c(1, 2))
ggsave_multiple(
  paste0("p_methods", c(".png", ".pdf")),
  plot = p_methods,
  path = here::here("report", "figures"),
  scale = 3.0,
  dpi = 400,
  width = 80,
  height = 80 * .6,
  units = "mm")
```

```{r}
tar_read(sim_fw) %>%
  filter(env_stoch == .6, S == 10, Z == 100) %>%
  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(h))) +
  geom_boxplot()
```

@@

```{r}
fw_values_bin <- list(
  ct_alive = c(low = .05, high = 0.30),
  avg_int_strength = c(low = .01, high = .1),
  w_avg_tlvl = c(low = 1, high = 2.3),
  resp_div = c(low = .25, high = 1)
)

pred_data_sr_fw <- pred_data %>%
  filter(
    ct_alive %in% fw_values_bin$ct_alive,
    resp_div %in% fw_values_bin$resp_div,
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% fw_values_bin$avg_int_strength,
    env_stoch == .1,
    w_avg_tlvl %in% fw_values_bin$w_avg_tlvl
    ) %>%
mutate(
  group_ct_alive = case_when(
    ct_alive == fw_values_bin$ct_alive["high"] &
      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "High",
    ct_alive == fw_values_bin$ct_alive["low"] &
      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
    ),
  group_avg_int_strength = case_when(
    ct_alive == fw_values_bin$ct_alive["low"] &
      avg_int_strength == fw_values_bin$avg_int_strength["high"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "High",
    ct_alive == fw_values_bin$ct_alive["low"] &
      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
    ),
  group_w_avg_tlvl = case_when(
    ct_alive == fw_values_bin$ct_alive["low"] &
      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["high"] ~ "High",
    ct_alive == fw_values_bin$ct_alive["low"] &
      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
    )) %>%
pivot_longer(starts_with("group_")) %>%
filter(!is.na(value)) %>%
mutate(
  name = str_remove(name, "group_"),
  resp_div_cat = str_replace_all(resp_div, resp_div_replacement()),
  variable_values = case_when(
    name == "ct_alive" & value == "Low" ~ fw_values_bin$ct_alive["low"],
    name == "ct_alive" & value == "High" ~ fw_values_bin$ct_alive["high"],
    name == "avg_int_strength" & value == "Low" ~ fw_values_bin$avg_int_strength["low"],
    name == "avg_int_strength" & value == "High" ~ fw_values_bin$avg_int_strength["high"],
    name == "w_avg_tlvl" & value == "Low" ~ fw_values_bin$w_avg_tlvl["low"],
    name == "w_avg_tlvl" & value == "High" ~ fw_values_bin$w_avg_tlvl["high"]
  )
)

@@

```{r}
pred_stab_comp_resp_div
p_pred_sr_resp_div +
  geom_point(
    data = pred_data_sr_fw %>%
      filter(richness == min(richness)) %>%
      mutate(name = var_replacement()[name]) %>%
      rename(variable = name),
    aes(color = NULL, fill = NULL)
  )

p_pred_sr <- plot_grid(
  p_pred_data_sr_fw + theme(legend.position = "right"),
  # Add location of the fw values of p_pred_data_sr_fw
  p_pred_sr_resp_div +
  geom_point(
    data = pred_data_sr_fw %>%
      filter(richness == min(richness)) %>%
      mutate(name = var_replacement()[name]) %>%
      rename(variable = name),
    aes(color = NULL, fill = NULL)
  ),
  nrow = 2,
  rel_heights = c(.7, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .7,
  units = "mm")
```

@@

sim_fw %>%
  filter(env_stoch == 0.3, rho %in% c(0, .5, 1)) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()
